What We Eval in the Shadows

### 2021-08-09 paper/main.tex
Fix intro
Fix description of assertion packages

A common use of \eval is to \emph{simplify interfaces} by letting users pass string
argument which can be parsed and evaluated in custom a environment. An example
is the \code{rARS} function from the \code{AdapSamp} package, shown below.

@@

\subsection{Custom Evaluation}
The \eval function is commonly used to customize the evaluation of expressions.
An example is the \code{assertthat} package's \code{see\_if} function which is used to
assert that the sequence of conditions supplied as arguments are true. It
evaluates the condition expressions one-by-one inside a \code{tryCatch} block and
produces an error at the first expression that returns \code{FALSE}. If the
expression itself produces an error, the error message is captured by the
enclosing \code{tryCatch} block and returned. The remaining expressions in the
sequence remain unevaluated. A similar pattern is used by the \code{checkmate}
package.

>>>>

A common use of \eval is to \emph{simplify interfaces} by letting users pass
string argument which can be parsed and evaluated in custom a environment. An
example is the \code{rARS} function shown below. This function is defined in the
\code{AdapSamp} package that implements sampling algorithms.

@@

Assertion packages such as \code{assertthat} provide functions to check pre and
post conditions and produce friendly error messages on failures. These
conditions are written as expressions which are evaluated using \eval. Consider
the \code{see_\if} function shown below. It accepts the conditions as arguments
to the \code{...} parameter. The code of these conditions is extracted using
\code{eval(substitute(alist(...)))}. The conditions are then evaluated
sequentially by the expression \code{eval(assertion, env)}, inside a
\code{tryCatch} block. If a condition evaluates to \code{FALSE}, the function
returns immediately with an error message, leaving the remaining conditions
unevaluated.

\begin{lstlisting}
see_if <- function(..., env = parent.frame(), msg = NULL) {
    asserts <- eval(substitute(alist(...)))
    for (assertion in asserts) {
      res <- tryCatch({
        eval(assertion, env)
      }, assertError = function(e) {
        structure(FALSE, msg = e$message)
      })
    ...
}

\end{lstlisting}
